\documentclass{resume}
\usepackage{latexsym}

\renewcommand{\categoryfont}{\sc}

%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter 
% 		will be reset to account for marginparsep]
% 
\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}
% 
% calculate other dimensions [textwidth and evensidemargin] 
% in function of oddsidemargin and marginparwidth: 
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
\setlength{\evensidemargin}{\oddsidemargin}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\addtolength{\textwidth}{-2\oddsidemargin}
\addtolength{\textwidth}{\marginparwidth}
\addtolength{\textwidth}{\marginparsep}

%
\setlength{\topmargin}{0in}
%
%
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\author{Leonardo Sandoval}

% ------ Address --------------------------------------------------------

\address{}
        {Abetos 544, Los Pinos\\
         Zapopan, Jalisco, M\'exico \\
         home   (+52) 33 38 13 06 65\\
         mobile (+52) 33 12 57 90 39\\
         \mbox{\small\tt leonardo\_gdl@yahoo.com.mx}}

\def\udg{University of Guadalajara}
\def\tub{\udg}
\def\inaoe{Instituto Nacional de Astrof\'{\i}sica, \'Optica y Electr\'onica}
\def\itesm{Tecnol\'ogico de Monterrey campus Monterrey}
\def\facty{Faculty of Computer Science}

\begin{document}
\maketitle

% ------- Education ---------------------------------------------------

\begin{category}{Education}
\citem{\inaoe}\\
MS in Computer Science. Thesis defended in January 2005.


\citem{\udg}\\
Diploma in Computer Science, August 1998.
\citem{Scholarships}
\begin{itemize}
\item Mexican-French Scientific Agreement (ANUIES-ECOS). January -- December 2003.
\item Mexican Science Sponsor (CONACYT). January 2001 -- December 2002.
\end{itemize}
\end{category}

% -------- Work experience --------------------------------------------

\begin{category}{Work \\experience}

\citem{Ooyala}
June 2011 -- present
Member of the \textit{Client Service Group}.
I am part of the CSG group which develop custom solutions to Ooyala clients. So far, I have participated in the development of
two important tools: 1) a tool to import large video content to Ooyala servers 2) SDK modules which allows clients to manage its videos
programatically. Last two months, a prototype Web portal was developed which allow users to purchase video content on-line. 

\citem{Texas Instruments}\\
Contractor: Dextra Technologies\\
August 2006 -- June 2011
\begin{itemize}
\item \textbf{Embedded Software Engineer} (August 2007 -- June 2011).\\
\textit{GStreamer} Texas Instruments group.\\
Our group creates and maintains GStreamer plugins for the OMAP family processors. Plugins are based on Texas-Instruments OpenMAX IL multimedia interface,
which in turn abstracts coding/decoding algorithms. I am focused mainly on video plugins and camera.\\
\item \textbf{Embedded Software Engineer} (August 2006 -- August 2007)\\
\textit{OpenMAX} Texas Instruments group.\\
Software developer for the OpenMAX IL Camera component for OMAP 2 family processors. Work mostly done on-site (Dallas, Texas, USA).\\
\end{itemize}

\citem\itesm\\
Part time, August 2006 -- January 2011
\begin{itemize}
\item \textbf{Web programmer} (August 2009 -- January 2011).\\
Full design and implementation of an Second factor authentication system using request's user agent. A complete functional prototype has been built.
\item \textbf{Web programmer} (August 2007 -- July 2008).\\	
Full design and implementation of a classification method for detecting intruders using keystrokes typing rhythm. 
\item \textbf{Research Assistant} (August 2006 -- December 2006).\\
An open-source statistical translation software called \textbf{Moses} was used to create a translation system	between a native language (Nahuatl) and Spanish.\\
\\
\end{itemize}
\end{category}

\newpage

\begin{category}{Research \\experience}
\citem{\inaoe}\\
\begin{itemize}
\item \textbf{Master thesis in Computer Astrophysics} (January 2001 -- December 2004).\\
Comparison between decay times of satellite galaxies using $n$-body numerical simulations and a two-body motion equation with dynamical friction. Several galaxy density profiles were compared. \\
Thesis partially done in Marseille, France.\\
Advisors:  Ivanio Puerari (INAOE, Mexico) and Lia Athanassoula (Observatoire de Marseille, France).\\
\item \textbf{Scientific Programmer} (August -- December 2000).\\
Comparison between two classification methods (\textsl{k}-nn and neural networks) using stellar spectra.\\
Advisor: Olac Fuentes \\
\\
\end{itemize}
\end{category}

% -------- Publication --------------------------------------------

\begin{category}{Talks}

\citembullet Extending Ruby with C Language. \\
University of Leiden, The Netherlands, June 2009. \\
%This talk was part of the Astrophysical Multipurpose Software Environment (AMUSE) first %workshop.

\citembullet Simulation of Decay Times of Satellite Galaxies using Semi-Analytical methods.\\
Proceedings of The National Convention of Astronomy 2003.\\
Instituto de Astronom\'{\i}a, UNAM. \\
Authors: Leonardo Sandoval, Lia Athanassoula and Jorge Villa
\end{category}

% ------- Skills ------------------------------------------------------
\\
\begin{category}{Skills}
\citembullet Programming languages: C, C++, Ruby, Python, PHP, Javascript, Java and Haskell
\citembullet Web frameworks: Ruby on Rails
\citembullet Content Management Systems: Drupal
\citembullet Databases: MySQL and  sqlite
\citembullet Operating systems: Mac OS X, Ubuntu and most Microsoft Windows family
\citembullet Version controllers: Git and IBM ClearCase
\end{category}
\\
\begin{category}{Languages}
\citembullet Native Spanish
\citembullet Fluent spoken/written English
\citembullet Fair \textbf{German}. ZDaF (Zertifikat Deutsch als Fremdsprache) obtained in Goethe-Institut, Guadalajara, Jalisco, Mexico (1996-1998)
\end{category}
\\

% ----- Hobbies ------------------------
\begin{category}{Hobbies}
\citembullet Mountain hiking
\citembullet Traveling
\citembullet Tennis
\end{category}
% -------- Reference --------------------------------------------
\\
\begin{category}{Reference} 
\citemnobullet Available on request.
\end{category}

\end{document}
